\question You want to go up a flight of stairs that has \texttt{n} steps. You can
either take 1 or 2 steps each time. How many different ways can you go up this
flight of stairs? Write a function {\tt count\char`_stair\char`_ways} that
solves this problem. Assume \texttt{n} is positive.

Before we start, what's the base case for this question? What is the simplest
input?
\begin{solution}[0.75in]
When there is only 1 step, there is only one way to go up the stair. When
there are two steps, we can go up in two ways: take a two-step, or take 2
one-steps.
\end{solution}
What do \texttt{count\char`_stair\char`_ways(n - 1)} and
\texttt{count\char`_stair\char`_ways(n - 2)} represent?
\begin{solution}[0.75in]
\texttt{count\char`_stair\char`_ways(n - 1)} represents the number of
different ways to go up the first $n-1$ stairs.
\texttt{count\char`_stair\char`_ways(n - 2)} represents the number of
different ways to go up the first $n-2$ stairs. Our base cases will take
care of the remaining 1 or 2 steps.
\end{solution}

\begin{blocksection}
Use those two recursive calls to write the recursive case:
\vspace{.5in}
\begin{lstlisting}
def count_stair_ways(n):
\end{lstlisting}
\begin{solution}[1.5in]
\begin{lstlisting}
    if n == 1:
        return 1
    elif n == 2:
        return 2
    return count_stair_ways(n-1) + count_stair_ways(n-2)
\end{lstlisting}
\href{https://youtu.be/VcZPTlE56G8?t=1h7m6s}{Video walkthrough (Leap of Faith)} \\
\href{https://www.youtube.com/watch?v=sgNGso3LhD8&index=6&list=PLx38hZJ5RLZd35oDi3TGz5p9DyyxU3WwA}{Video Walkthrough (Diagramming Trees)}
\end{solution}
\end{blocksection}
